Designing Laboratory Notebooks for Managing Software-based Scientific Studies

### 2023-09-05 Dhruv-Dubey-LabNotebooks/Paper.tex
add color to edited text

\section{LABORATORY NOTEBOOKS FOR COMPUTATIONAL EXPERIMENTS}
Since computational work often involves coding, simulations, and data
analysis using software tools, the lab notebook is best maintained in
electronic format, and could include a combination of repositories,
spreadsheets, text, and markdown formats. 
For reasons discussed previously\footnote{\url{https://www.youtube.com/watch?v=fWpI4S_dvhc}}, the use of some form of
lab notebook in computational science has several challenges.
However, fundamental sets of activities that must be recorded are fairly
simple to enumerate.

@@

An example of a workflow that might be encountered by a developer who is also a user of the code for doing scientific investigations is shown in Figure \ref{fig:case-study-example}a. Such developers may perform regular testing of the physics and infrastructure components, keep track of the performance changes, and conduct scientific experiments at the same time.  The collection of lab notebooks \cite{Lab-Notebooks} described in Figure \ref{fig:case-study-example}b provides a good example of what may be done in such circumstances. These notebooks are all seeded from a general notebook \cite{Multiphysics-Simulations} being maintained by the developer in question. In this instance, the developer is simultaneously conducting the following experiments,

@@

The process of seeding and managing these notebooks is implemented using a lightweight command line tool, Jobrunner \cite{Jobrunner}, that enforces a directory-based inheritance for application configurations encoded in shell scripts to manage computational experiments. The directory tree is designed to split different shell commands that set up the software stack and simulation in an optimal way. For instance, a combination of {environment.sh} and {setupAMReX.sh} is used to configure AMReX most suitably for the experiment. Here, {environment.sh} documents and sets variables that store compiler information and installation location of different libraries, and {setupAMReX.sh} stores information specific to building AMReX with the necessary options. The {Jobfiles} that exist at every level of the tree encode information that Jobrunner can use to stitch together these bash files to perform different tasks. 
%
\begin{figure}
\begin{minted}[
    gobble=1,
    frame=single,
  ]{yaml}
  # Location:
  # Experiment
  job:
    setup:
        - environment.sh
    submit:
        - environment.sh

@@

Jobrunner hides error-prone individual steps of the experiments while allowing organized and explicit documentation of configuration options that can be easily modified by editing the shell scripts. The directory tree in Figure \ref{fig:dirtree} can be easily modified and redesigned based on the requirements of the experiments to include markdown notes and analysis files. For full functionality and documentation for Jobrunner see A. Dhruv \cite{Jobrunner}.
%
\begin{figure}
\begin{minted}[
    gobble=8,
    frame=single,
  ]{bash}
        # Setting up software and dependencies
        jobrunner setup software/amrex
        jobrunner setup software/flashx

>>>>

\section{LABORATORY NOTEBOOKS FOR COMPUTATIONAL EXPERIMENTS}
Since computational work often involves coding, simulations, and data
analysis using software tools, the lab notebook is best maintained in
electronic format, and could include a combination of repositories,
spreadsheets, text, and markdown formats. 
{\color{red} For reasons discussed previously\footnote{\url{https://www.youtube.com/watch?v=fWpI4S_dvhc}}}, the use of some form of
lab notebook in computational science has several challenges.
{\color{red}However, fundamental sets of activities that must be recorded are fairly
simple to enumerate}.

@@

An example of a workflow that might be encountered by a developer who is also a user of the code for doing scientific investigations is shown in Figure \ref{fig:case-study-example}a. Such developers may perform regular testing of the physics and infrastructure components, keep track of the performance changes, and conduct scientific experiments at the same time.  {\color{red}The collection of lab notebooks \cite{Lab-Notebooks} described in Figure \ref{fig:case-study-example}b provides a good example of what may be done in such circumstances}. These notebooks are all seeded from a general notebook \cite{Multiphysics-Simulations} being maintained by the developer in question. In this instance, the developer is simultaneously conducting the following experiments,

@@

The process of seeding and managing these notebooks is implemented using a lightweight command line tool, Jobrunner \cite{Jobrunner}, that enforces a directory-based inheritance for application configurations encoded in shell scripts to manage computational experiments. The directory tree is designed to split different shell commands that set up the software stack and simulation in an optimal way. For instance, a combination of {environment.sh} and {setupAMReX.sh} is used to configure AMReX most suitably for the experiment. Here, {environment.sh} documents and sets variables that store compiler information and installation location of different libraries, and {setupAMReX.sh} stores information specific to building AMReX with the necessary options. {\color{red} The {Jobfiles} that exist at every level of the tree encode information that Jobrunner can use to stitch together these bash files to perform different tasks.} 
%
\begin{figure}
\begin{minted}[
    gobble=1,
    frame=single,
  ]{yaml}
  # Location:
  # Experiment
  job:
    setup:
        - environment.sh
    submit:
        - environment.sh

@@

Jobrunner hides error-prone individual steps of the experiments while allowing organized and explicit documentation of configuration options that can be easily modified by editing the shell scripts. The directory tree in Figure \ref{fig:dirtree} can be easily modified and redesigned based on the requirements of the experiments to include markdown notes and analysis files. {\color{red}For full functionality and documentation for Jobrunner see A. Dhruv \cite{Jobrunner}.}
%
\begin{figure}
\begin{minted}[
    gobble=8,
    frame=single,
  ]{bash}
        # Setting up software and dependencies
        jobrunner setup software/amrex
        jobrunner setup software/flashx
